RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-28 discussion.tex
yes

{\bf Security.}
It is essential to provide security in an environment that encourages
collaboration and data publishing.  RCloud uses an object capability model
\cite{Miller:2006:RCT}
recently added to the Rserve protocol \cite{Urbanek:2003:AFW}
that prevents unauthenticated clients from making
unauthorized calls to the RCloud runtime environment.

>>>>

{\bf Security.}
It is essential to provide security in an environment for
collaboration and data publishing. To provide some
protection for RCloud workbooks in an organization's intranet,
RCloud uses an object capability model
\cite{Miller:2006:RCT}
recently added to the Rserve protocol \cite{Urbanek:2003:AFW}
that prevents unauthenticated clients from making
unauthorized calls to the RCloud runtime environment.
